---
title: "My first R markdown"
subtitle: "Created fully by myself"
author: "Viktória Kónya"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
    prettydoc::html_pretty:
      theme: cayman
      highlight: github

---

# Aim

In this project I am practicing R markdown features.

I would like to:

1. understand R markdown
2. learn new things
3. create a nice document

# Theme

To change the theme of the document I am using [Prettydocs](https://prettydoc.statr.me/).

# Codes

I include a code chunk with a comment in it.

```{r}
# I am the comment :D
```

I also say hello to the world with a `print()` and for that I am only showing the output of the code.

```{r}
"Hello World!"
```

# Tables

With kableExtra I show the first 5 rows of the **ChickWeight** dataset. For this I will use the [kableExtra](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html) package which I imported in a separate chunk.

For the table I used the *classic* style.

```{r echo = F}
library(kableExtra)
dt <- ChickWeight[1:5, ]
kable(dt) %>%
  kable_classic(full_width = F)
```

# Plots

I included one plot. It need to:

* be aligned to the center
* have a size of 70%
* hide the codes creating the plot
* hide warning message


```{r echo = F}
library(ggplot2)
ggplot(cars, aes(x=speed, y=dist)) +
  geom_point(color = "green4") +
  labs(title = "Chart of cars",
       x = "Speed",
       y = "Distance") +
  theme_bw()
```





