---
title: "Week 12 - Extra"
author: "Viki - Misi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
    prettydoc::html_pretty:
      theme: cayman
      highlight: github
      toc: TRUE

---

```{r setup, include = F}

knitr::opts_chunk$set(warning = F, message = F) 

```


## Snippets

**Code Snippets** let us easily insert and execute predefined pieces of code that are commonly used in our work. Code Snippets are not just available for R but for many other languages.

1. In RStudio, we can browse and define snippets under Tools -> Global Options... -> Code -> Edit Snippets window
2. When typing code, the snippet will appear as an auto-complete option (similar to function names) if we type the first few letters of its name.
3. Use Shift+Tab to insert the snippet immediately or pick the snippet from the auto-complete list (by clicking or scrolling on it and pressing Tab).

Let's create a new code snippet with the following command and then call the snippet.

```{r snippet, eval = F}

############################################################
# Title: 
# Created by: <Your name>
# Date: 
# Notes: 
############################################################  

# Clear environment
rm(list=ls())
.rs.restartR()

# Load packages

# Define path
data_in <- paste0(getwd(), "/input")
data_out <- paste0(getwd(), "/output")

# Import data
df <- read.csv(paste0(data_in,"my_dataset.csv"))

```


## Pacman package

The pacman package is an R package management tool.

```{r pacman-install}

if (!require("pacman")) {
  install.packages("pacman")
}

```

We can install and load multiple R packages using the **p_load** function.

In base R if we want to install and load the required packages we need to type in the following long command:

```{r pacman1, eval = F}

if (!require("tidyverse")) {
  install.packages("tidyverse")
}

if (!require("data.table")) {
  install.packages("data.table")
}

if (!require("janitor")) {
  install.packages("janitor")
}

if (!require("kableExtra")) {
  install.packages("kableExtra")
}

if (!require("lubridate")) {
  install.packages("lubridate")
}

library(tidyverse)
library(data.table)
library(janitor)
library(kableExtra)
library(lubridate)

```

While using **pacman** we can do the same with one line of code:

```{r pacman2}

library(pacman)
pacman::p_load(tidyverse, data.table, janitor, kableExtra, lubridate)

```


## Extract dependencies

We can use the **NCmisc** package to identify which packages (and which functions) are actually being used by an R file. 

First we need to extract the R code from the Rmd document:

```{r extract-code}

pacman::p_load(knitr)
purl(input = "C:/Users/User/Documents/GitHub/Coding-Practice-With-R-2022-2023/week-10/week-10.Rmd",
     output = "C:/Users/User/Documents/GitHub/Coding-Practice-With-R-2022-2023/week-10/week-10.R")

```

The **list.functions.in.file()** function parses all functions used in an R script and then lists them by package. 

```{r list-dependencies}

pacman::p_load(NCmisc, kableExtra)
dependencies <- list.functions.in.file('C:/Users/User/Documents/GitHub/Coding-Practice-With-R-2022-2023/week-10/week-10.R', alphabetic = TRUE)

kable(dependencies) %>%
  kable_styling(full_width = F, font_size = 11)

```


