---
title: "Week 5 - Tasks"
author: "Viki - Misi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
    toc: yes

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.pos = 'H') 

```

## Recap tasks use base R functions
```{r}
library(rtsdata)
ticker <- 'TSLA'
df <- data.frame(ds.getSymbol.yahoo(ticker, from = (Sys.Date() - 250), to = Sys.Date()))
head(df)
```


### Remove the ticker name of the header 
```{r, echo=FALSE}
# Your code comes here
```


### Transform the header to lowercase
```{r, echo=FALSE}
# Your code comes here
```


### Create a date column out of the rownames
```{r, echo=FALSE}
# Your code comes here
```

### Create simple index to the rownaes
```{r, echo=FALSE}
# Your code comes here
```


### Create a column called `low_high_diff` and calculate the daily percentage change between the high and low value.
```{r, echo=FALSE}
# Your code comes here
```

### Round the new value to two digits
```{r, echo=FALSE}
# Your code comes here
```


## Dplyr tasks

Load the `nycflights13` package and **write code**, to reproduce the same result that showed here while you answer the questions!

```{r, message=FALSE}

# comment multiple lines 
# ctrl + shift + c

# Clear environment
rm(list=ls())

# install.packages('nycflights13')
library(nycflights13)
library( tidyverse )

```

Help
```{r}
# df %>%
#   filter() %>% 
#   group_by()%>%
#   summarise( ) %>%
#   arrange()%>%
#   head()
```


### Which airplane was in the air the most time?

```{r, dplyr-1, echo=FALSE}

# Your code comes here

```

### What is the best carrier based on arrival delay (where the average `arr_delay` is the least, it can be negative)? Also show the number of flights.

```{r, dplyr-2}

# Your code comes here

```

### What is the name of the arline company which had the most arrival delay on average in August?

```{r, dplyr-3}

# Your code comes here

```


### Who is the manufacturer of the flights that flow the most times from `EWR` and how much times it flow?

```{r, dplyr-4}

# Your code comes here

```


### How many seats does the aeroplane have which flow the most times from `JFK` to `MCO`?

```{r, dplyr-5}

# Your code comes here

```


## Ggplot tasks

Use the first 1000 rows of flights datasets and name your new dataframe as 'df'.

```{r}

# Your code comes here
  
```

### Reproduce the ggplots! 


```{r, ggplot-1}

# Your code comes here

```

```{r, ggplot-2}

# Your code comes here

```


```{r, ggplot-3}

# Your code comes here

```

```{r, ggplot-4}

# Your code comes here

```

```{r, ggplot-5}

# Your code comes here

```

