---
title: "Week 5 - Tasks"
author: "Viki - Misi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
    toc: yes

---

```{r setup, include=FALSE}
library(kableExtra)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.pos = 'H') 

```


## Recap tasks use base R functions
```{r}
library(rtsdata)
ticker <- 'TSLA'
df <- data.frame(ds.getSymbol.yahoo(ticker, from = (Sys.Date() - 250), to = Sys.Date()))
head(df) %>% kbl()
```


### Remove the ticker name of the header 
```{r, echo=FALSE}
names(df) <- gsub(paste0(ticker, '.'), '',names(df), fixed = T)
head(df) %>% kbl()
```


### Transform the header to lowercase
```{r, echo=FALSE}
names(df) <- tolower(names(df))
head(df) %>% kbl()
```


### Create a date column out of the rownames
```{r, echo=FALSE}
df$date <- as.Date(row.names(df))
head(df) %>% kbl()
```

### Create simple index to the rownames
```{r, echo=FALSE}
row.names(df) <- 1:nrow(df)
head(df) %>% kbl()
```


### Create a column called `low_high_diff` and calculate the daily percentage change between the high and low value.
```{r, echo=FALSE}
df$low_high_diff <- ((df$high/df$low)-1)*100
head(df) %>% kbl()
```

### Round the new value to two digits
```{r, echo=FALSE}
df$low_high_diff <- round(df$low_high_diff,2)
head(df) %>% kbl()
```





## Dplyr tasks

Load the `nycflights13` package and **write code**, to reproduce the same result that showed here while you answer the questions!

```{r, message=FALSE}

# comment multiple lines 
# ctrl + shift + c

# Clear environment
rm(list=ls())

# install.packages('nycflights13')
library(nycflights13)
library( tidyverse )

```

Help
```{r}
# df %>%
#   filter() %>% 
#   group_by()%>%
#   summarise( ) %>%
#   arrange()%>%
#   head()
```


### Which airplane was in the air the most time?

```{r, dplyr-1, echo=FALSE,message=F, warning=FALSE}

flights %>%
  filter(!is.na(tailnum)) %>% 
  group_by(tailnum)%>%
  summarise('in_air'= sum(air_time) ) %>%
  arrange(-in_air) %>%
  head(1)

```

### What is the best carrier based on arrival delay (where the average `arr_delay` is the least, it can be negative)? Also show the number of flights.

```{r, dplyr-2, echo=FALSE, message=F, warning=FALSE}

# number of flights from origin
flights %>%
  group_by(carrier)%>%
  summarise('mean_arr_delay'=mean(arr_delay, na.rm = T), 
            'n_flights'= n()) %>%
  arrange(mean_arr_delay) %>% 
  head(1)

```

### What is the name of the arline company which had the most arrival delay on average in August?

```{r, dplyr-3, echo=FALSE, message=F, warning=FALSE}

t <- 
flights %>%
  filter(month==8) %>% 
  group_by(carrier)%>%
  summarise('mean_delay'=mean(arr_delay, na.rm = T)) %>% 
  arrange(-mean_delay) %>% 
  head(1) 

merge(t, airlines, by = 'carrier') %>% 
  select(name)

```


### Who is the manufacturer of the flights that flow the most times from `EWR` and how much times it flow?

```{r, dplyr-4, echo=FALSE}
t <- 
flights %>% 
  filter(!is.na(tailnum),
         origin%in%c('EWR')) %>% 
  group_by(tailnum) %>% 
  summarise('flight_times'= n()) %>% 
  arrange(-flight_times) %>% 
  head(1)

merge(t,planes, by = 'tailnum' ) %>% 
    select(tailnum, manufacturer, flight_times)

```

