---
title: "Week 5 - Rio"
author: "Viki - Misi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
    toc: yes

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.pos = 'H') 

```


```{r libraries, echo = F, include = F}

# Clear environment
rm(list=ls())

# Import libraries
library(kableExtra)
library(tidyverse)

# set working directory
setwd('C:/Users/User/Documents/GitHub/Coding-Practice-With-R-2022-2023/week-5')

# Define path
data_in <- paste0(getwd(), "/data_in")
data_out <- paste0(getwd(), "/data_out")

```

## Import and export files with **rio** package

{rio} is a wrapper around different packages that import/export data in different formats. This package is nice because you don’t need to remember which package to use to import different file formats (SAS, STATA, JSON datasets etc.). 

Read the documentation here: [Documentation](https://cran.r-project.org/web/packages/rio/vignettes/rio.html)

```{r}

if (!("rio" %in% installed.packages())) {
  install.packages("rio")
}
library(rio)

```

### XLSX

```{r rio-xlsx-import}

iris_xlsx <- import(file = paste0(data_in, "/iris.xlsx"))
kable(head(iris_xlsx)) %>%
  kable_styling(full_width = F)

```

```{r rio-xlsx-export}

# Export to one sheet
virginica <- subset(iris_xlsx, Species == "virginica")
export(virginica, file = paste0(data_out, "/virginica.xlsx"))

```

```{r rio-xlsx-export-multi}

# Or export multiple sheets
export(list(virginica = subset(iris_xlsx, Species == "virginica"), 
            setosa = subset(iris_xlsx, Species == "setosa")), paste0(data_out,"/iris_xlsx_multi.xlsx"))

```

### SAV 

```{r rio-sav-import}

iris_sav <- import(file = paste0(data_in, "/iris.sav"))
kable(head(iris_sav)) %>%
  kable_styling(full_width = F)

```

With 'tidyverse' ('dplyr') package we can also add the export() to a pipe operator

```{r rio-sav-export}

iris_sav %>%
  filter(Species == "setosa") %>%
  export(paste0(data_out, "/virginica.sav"))

```

### JSON

```{r rio-json-import}

iris_json <- import(file = paste0(data_in, "/iris.json"))
kable(head(iris_json)) %>%
  kable_styling(full_width = F)

```

```{r rio-json-export}

virginica <- subset(iris_json, Species == "virginica")
export(virginica, file = paste0(data_out, "/virginica.json"))

```

### Convert datasets

```{r rio-convert-xlsx-json}

# Convert xlsx to JSON
convert(paste0(data_in, "/iris.xlsx"), paste0(data_out, "/iris_converted.json"))

```

```{r rio-convert-xlsx-json-2}

# Check converted dataset
iris_json_converted <- import(paste0(data_out, "/iris_converted.json"))
kable(head(iris_json_converted)) %>%
  kable_styling(full_width = F)

```

