---
title: "Week 7 - Functions"
author: "Viki - Misi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction to conditional statements:  **if**,  **if ... else** and **if ... else if ... else** statements, the **ifelse()** function

### The if statement

We can evaluate whether a condition is met with the **if** statement.

| The syntax of if statement is:
|
| if (**condition**) {
|     **statement**
| }

We check whether the value of the 'number' object is equal to 1:

```{r if1}
# Assign a value to the number object
number <- 1

if (number == 1) {
  print("It is 1.")
}
```

We check whether the value of the 'number' object is equal to 0:

```{r if2}

if (number == 0) {
  print("It is 0.")
}

```

In case the condition is not met nothing is returned.

### The if ... else statement

We can evaluate which a condition is met with the **if ...else** statement.

| The syntax of if ... else statement is:
|
| if (**condition**) {
|     **statement1**
| } else {
|     **statement2**
| }

We check whether the value of the 'number' object is equal to 1:

```{r if_else1}

if (number == 1) {
  print("It is 1.")
} else {
  print("It is not 1.")
}

```


### The if ... else if ... else statement

We can also add multiple conditions with the **else if** statement.

| The syntax of if ...else if ... else statement is:
|
| if (**condition1**) {
|     **statement1**
| } else if (**condition2**) {
|     **statement2**
| } else if (**condition3**) {
|     **statement3**
| } else {
|     **statement4**
| }

And we can create a function from it: 

```{r if_elseif_else1}

check_number_complex <- function(number) {
  if (number == 1) {
    print("It is 1.")
  } else if (number == 0) {
    print("It is 0.")
  } else if (class(number) != "numeric") {
    print("It is not a number!")
  } else {
    print("It is neither 1 nor 0. But it is a number.")
  }
}

```
And then call the function:

```{r if_elseif_else1_eval}

check_number_complex(1)
check_number_complex(0)
check_number_complex(100)
check_number_complex("Misi")

```

Or we can add multiple conditions within one if-else branch:

| The syntax of if ...else with multiple conditions within one branch:
|
| if (**condition1 & condition2**) {
|     **statement1**
| } else {
|     **statement2**
| }
|
| if (**condition1 | condition2**) {
|     **statement1**
| } else {
|     **statement2**
| }

```{r if_else2}

check_number_or <- function(number) {
  if (number == 1 | number == 0) {
    print("It is 1.")
  } else {
    print("It is neither 1 nor 0.")
  }
}

```

```{r if_else2_eval}

check_number_or(1)
check_number_or(100)

```

### The ifelse() function

We can also evaluate whether a condition is met with the **ifelse()** function

| The syntax of ifelse() funtion is:
|
| ifelse(conditon, statement1, statement2)

```{r ifelse1}

ifelse(number == 1, "It is 1.", "It is not 1.")
ifelse(number == 0, "It is 1.", "It is not 1.")

```
# Conditional statements tasks

Create a function that evaluates whether a number is divisible by 2 and/or 3. It should have 4 outcomes: the number is divisible by 2, the number is divisible by 3, the number is divisible by both 2 and 3, the number is neither divisible by 2 nor by 3. Check your function with 6, 10, 15, and 17.

```{r conditional_task1}

# Your code comes here.



```

Reproduce the check_number_complex() function but now use the ifelse() function.Check your function with 1, 0, "Misi" and 10.

```{r conditional_task2}

# Your code comes here.


```
# For loops

### Simple for loop

We can iterate over a sequence with the **for** loop.

| **The syntax of a simple for loop:**
|
| for (i in vector) {
|   statement(s) with the [i] index 
| }

Let's create a sequence of even numbers from the odd_numbers vector!

```{r for_simple1}

odd_numbers <- seq(1, 10, by = 2)
odd_numbers

```

```{r for1_simple2}
even_numbers <- NA

for (i in 1:length(odd_numbers)) {
  even_numbers[i] <- odd_numbers[i] + 1
}
even_numbers

```

Note that we need to create an empty vector for the even numbers in advance!

### For loop with dataframes

We can iterate over the columns of a data frame with the **for** loop:

```{r for_df1}

df <- data.frame(numbers = 1:5, letters = c("a", "b", "c", "d", "e"),
                 stringsAsFactors = F)
df

```

Let's multiply the values in the numbers column with 2 and concatenate "a" to the items of the letters column!

```{r for_df2}

for (i in 1:nrow(df)){
  df$numbers[i] <- df$numbers[i] * 2
}
df

```

```{r for_df3}

for (j in 1:nrow(df)){
  df$letters[j] <- paste0(df$letters[j], "a")
}
df

```

### For loops with conditional statements

We can also combine for loops and conditional statements.

```{r for_conditional1}

for (i in 1:nrow(df)) {
  if (df$number[i]%%4 == 0) {
    print("It is divisible by 4.")
  }
  else {
    print("It is not divisible by 4 but it is an even number.")
  }
}

```
And we can create a function from the for loop.

```{r for_conditional2}

check_divisibility_2 <- function(input_df, column) {
  for (i in 1:nrow(input_df)) {
    if (input_df[i, column]%%4 == 0) {
      print("It is divisible by 4.")
    }
    else {
      print("It is not divisible by 4 but it is an even number.")
    }
  }
}
  
check_divisibility_2(df, number)

```

# Introduction to functions

| **The syntax of a simple function:**
|
| function_name <- function(**arguments (with default value)**) { 
|     **Do something**
|     return(output)
| }

We can create functions in the main script and save it as an object:

```{r functions1}

exponent_multiply <- function(x = 2, y = 2, z = 2) {
  print(paste0(x, " raised to the power of ", y, " and multiplied by ", z, 
              ". The result is ", x ^ y * z, "."))
}

exponent_multiply(2, 4, 6)

```
Or we can call the functions from an external script:

```{r functions2}

source("week-7-functions.R")

greet_person_external("Hola", "Amigos")
greet_person_random()

```

If we don't specify the return value it returns with the result from the last operation.


```{r functions3}

exponent <- function(x, y = 2) {
  x ^ y
  x + 2
}

exponent(4,2)
```


```{r functions4}
exponent <- function(x, y = 2) {
  z = x ^ y
  n = x + 2
  return(z)
}

exponent(4,2)

```

# Functions and for loops tasks


Create a dice function that will take the number of sides of the dice as input and prints out the results from rolling the dice.

```{r functions_task1}

# Your code comes here


  
```

Create a function that:

* First evaluates whether the type of the column is integer or not.
* If it is an integer type column then it iterates over the values of it and multiplies each item with a pre-defined multiplier. Finally it prints out the resulting dataframe.
* If it is not an integer type column then it prints out that "This is not an integer type column".

The function should have 3 input arguments: the name of the input dataframe, the name of the column and the value of the multiplier. Check your function with the following inputs: (df, "numbers", 2) and (df, "letters", 3)

```{r functions_task2}

# Your code comes here

# df_new <- df_multiply(df, "numbers", 2)

```

