---
title: "Week-10"
author: "Viki-Misi"
date: "November 24, 2022"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r}
# source('lotto.R')
```

# Lotto task

Make function for lotto simulation and compare your results with the user input
```{r}
# we have a function that ask numbers from users
min_number <- 1
max_number  <- 90
number_of_choose <- 5

get_numbers_from_user <- function(min_number, max_number, number_of_choose) {
  numbers <- c()
  while (length(numbers)<number_of_choose) {
    t_number <- readline(prompt = paste0('Please give me the ', length(numbers)+1 ,'. number between ' , min_number, ' and ', max_number, '. Your number:'))
    if (grepl('.',t_number, fixed = T) | grepl(',',t_number, fixed = T)   ) {
      print(paste0('Please write integers between: ',min_number, ' and ', max_number, '!' ))
      next()
    }
    t_number  <- as.integer(t_number)
    if (t_number%in% numbers) {
      print(paste0(t_number, ' is already in your numbers!' ))
      next()
    }
    if (is.na(t_number) ) {
      print('Please write numbers number')
    }
    else {
      if (t_number>=min_number & t_number<=max_number ) {
        numbers <- c(numbers, t_number)
      } else{
        print(paste0('The number should be between: ', min_number, ' and ', max_number, '!' )) 
      }
    }
  }
  numbers <- sort(numbers)
  return(sort(numbers))
}

# get_numbers_from_user(1,90, 5)
```






```{r, include=T}

library(tidyverse)
library(data.table)
library(janitor)
library(kableExtra)
library(lubridate)

```

## Get the data
You can get the data from [Github](https://github.com/misrori/ceu-ba-mentoring-priv/tree/2021-2022/week-7/Data).

```{r import}

IMDB_50 <- read.csv()
IMDB_top200 <- read.csv()

```

## Merge the data sets
We have our data in two tables, so lets merge them together.

```{r merge}


```


## Drop unnecessary columns

Delete the followings:

* everything with *tomato*
* Poster
* Website
* Response
* imdbID

```{r drop-columns}

df <- df %>%
  
```

## Deal with column names

Rename some columns

* *X* to **IMDB_rank**
* *Runtime* to **Lengt_min**

```{r column-names1}

df <- df %>%
 

```


Make sure all names are lower case and are separeted by _ in case needed.

<details>
  <summary>Hint</summary>
  Check out **janitor** package.
</details>

```{r column-names2}


```

## Change data types


The `IMDB rank` should be NOT numeric.

```{r change-data-types2}


```


`metascore`, `imdb_votes` and `box office` should be numeric.

<details>
  <summary>Hint 1</summary>
  Keep only numbers in the column.
</details>

<details>
  <summary>Hint 2</summary>
  Substitute N/A values with the proper ones.
</details>

```{r change-data-types3}

df <- df %>% 
  
# gsub("[ab#]", "","sdgefgroasfdsbbbsafds####asfe")
```


## Start looking at columns

#### `length_min`

This should be numeric, without the *min* word.

```{r look-at-data2}

df <- df %>% 

```


#### `genre`

There are 1, 2 or 3 genre given for a film, to be able to deal with this we need them in different columns. Also pay attention to extra white spaces!

```{r look-at-data3}

df <- df %>% 

```


#### `director`

Keep only the first one listed.

```{r look-at-data4}

df <- df %>% 
  
```


#### `ratings_value`

Should be numeric so /10  is not needed.

```{r look-at-data8}

df <- df %>% 

```

#### `Awards`

This will be the difficult part.

As a first step create 4 new columns:

* wins
* nominations
* oscars
* oscar nominations




Create 4 functions to extract the number from the text in the `awards` column. 

<details>
  <summary>Hint 1</summary>
  Use `grepl()` to determine if the word *wins/nominations.|nomination./Won&Oscar/Nominated&Oscar* are in the text.
</details>

<details>
  <summary>Hint 2</summary>
  Use `strsplit()` to create a list of the words.
</details>

<details>
  <summary>Hint 3</summary>
  Make sure you deal with *wins.* vs *wins* or *nominations.* vs *nomination.*.
</details>

<details>
  <summary>Hint 4</summary>
  Use `which()` to find on which place the searched word (*wins/nominations./Won/Nominated*) is, and return the value from the list before this. In case the searched word is not in the sentence return NA.
</details>


```{r, functions }



```


Loop through the rows of the data frame and get the number of wins and nominations in the 4 predefined columns using the functions created.

```{r functions2}



```





