---
title: "Week 6 - Tasks"
author: "Viki - Misi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
    toc: yes

---

```{r setup, include=FALSE}
library(kableExtra)
library(nycflights13)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.pos = 'H') 

```


### How many seats has the airplane which flow the most times from `JFK` to `MCO`?

```{r, dplyr-5, echo=FALSE}

flights %>% 


```

## The best carriers based on arriving (on average the arr_delay is the least), colors= limegreen and cyan4
```{r, echo=FALSE, message=F, warning=FALSE}
# number of flights from origin
flights %>%

```



## Average arrival delay by destinations **name** in August

```{r, echo=FALSE, message=F, warning=FALSE}

flights %>%


```


## The most popular airiles **name** from `JFK`
```{r, echo=FALSE}

flights %>%


```




## Ggplot tasks

Use the first 1000 rows of flights datasets 

```{r}
df <- flights %>% head(1000)
```


### Reproduce the ggplots! 

```{r, echo=FALSE, warning=F, message=F, warning=FALSE}


# http://statseducation.com/Introduction-to-R/modules/graphics/cont/

#1
ggplot(df, aes(x=distance, y= arr_delay))

```


```{r, echo=FALSE, warning=F, message=F, warning=FALSE}  



```


```{r, echo=FALSE, warning=F, message=F, warning=FALSE}  


```


```{r, echo=FALSE, warning=F, message=F, warning=FALSE}  

```


```{r, echo=FALSE, warning=F, message=F, warning=FALSE}  
 
 
```


Violin plot with theme_void
```{r, echo=FALSE, warning=F, message=F, warning=FALSE}  
 
```

